\texttt{ggmatplot}: An R package for data visualization on wide-format data

### 2022-05-07 Paper/paper.Rmd
modify the comments in the draft

*Regarding the question from Francis, I don't know if long format or wide format data is well defined in the literature. If it is, we definitely can mention it. If not, do we need to define it? --commented by XL*

@@

*In example 1, should X lab be restaurant or one type rating? The one made by ggmatplot is different from the one made by ggplot. Currently, the plot does not show a clear relationship between various types and the overall rating. Is it better to compare the ratings among restaurants?  -- commented by XL*

@@

*Now the color and fill has been removed by default for boxplot by default, there is no legend. We may need to change the demonstration of Example 2. -- commented by XL*
*Another question is that only the github version has such setting. Do I need to submit the new version to CRAN? -- commented by XL*

>>>>

*Regarding Francis' question, I don't know if the long format or wide format data are well defined in the literature. If it is, we definitely can mention it. If not, do we need to define it? --commented by XL*

@@

*In example 1, should X lab be restaurant or rating? The one made by ggmatplot is different from the one made by ggplot. Currently, the plot does not show a clear relationship between various types and the overall rating. Is it better to compare the ratings among restaurants?  -- commented by XL*

@@

*Now the color and fill has been removed for boxplot. So by default, there is no legend. We may need to change the demonstration of Example 2. -- commented by XL*
*Another question is that only the github version has such setting. Do I need to submit the new version to CRAN? -- commented by XL*

### 2022-05-07 Paper/paper.tex
modify the comments in the draft

\emph{Regarding the question from Francis, I don't know if long format
or wide format data is well defined in the literature. If it is, we
definitely can mention it. If not, do we need to define it? --commented
by XL}

@@

\emph{In example 1, should X lab be restaurant or one type rating? The
one made by ggmatplot is different from the one made by ggplot.
Currently, the plot does not show a clear relationship between various
types and the overall rating. Is it better to compare the ratings among
restaurants? -- commented by XL}

@@

\emph{Now the color and fill has been removed by default for boxplot by
default, there is no legend. We may need to change the demonstration of
Example 2. -- commented by XL} \emph{Another question is that only the
github version has such setting. Do I need to submit the new version to
CRAN? -- commented by XL}

>>>>

\emph{Regarding Francis' question, I don't know if the long format or
wide format data are well defined in the literature. If it is, we
definitely can mention it. If not, do we need to define it? --commented
by XL}

@@

\emph{In example 1, should X lab be restaurant or rating? The one made
by ggmatplot is different from the one made by ggplot. Currently, the
plot does not show a clear relationship between various types and the
overall rating. Is it better to compare the ratings among restaurants?
-- commented by XL}

@@

\emph{Now the color and fill has been removed for boxplot. So by
default, there is no legend. We may need to change the demonstration of
Example 2. -- commented by XL} \emph{Another question is that only the
github version has such setting. Do I need to submit the new version to
CRAN? -- commented by XL}
